Reflections on reflection for \\ intuitionistic set theories

### 2019-02-01 paper-reflection.tex
typo

If the answer is in the negative, as is most likely, then no conservative
extension could include a constant symbol~$\SS$ should that~$\SS$-relativized
truth is the same as absolute truth.

>>>>

If the answer is in the negative, as is most likely, then no conservative
extension could include a constant symbol~$\SS$ such that~$\SS$-relativized
truth is the same as absolute truth.
